---
title: "Performance Summary"
output:
  html_document: default
vignette: >
  %\VignetteIndexEntry{Performance Summary}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8} 
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

## Time and resources spent in the workflow

240 GB memory and 3 cpus were used. Medium: n_cells: 94256, large: n_cells: 168860

CPU mean
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("CPU_mean.csv")
```

Memory max
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("MEM_mean.csv")
```

Time
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("time.csv")
```

## DelayedArray & `modelGeneVarByPoisson()`

```{r, echo = TRUE, message=FALSE, eval=FALSE}
# autoBlockSize
library(Rcollectl)
times_delayed_block_size <- lapply(67108864L * 2L^(0:5), function(i) {
    gc()
    setAutoBlockSize(i)
    bpp <- SerialParam()
    system.time({
    	id <- cl_start(paste0("AutoBlockSize_", i))
        dec_delay <- modelGeneVarByPoisson(
            sce_delay, block=sce_delay$sample, BPPARAM=bpp
        )
        cl_stop(id)
    })
})

# cpu
setAutoBlockSize(.Machine$integer.max)
times_delayed <- lapply(1:5 * 2L, function(i) {
    message(i)
    bpp <- MulticoreParam(i)
    system.time({
        id <- cl_start(paste0("cpu_", i))
        dec_delay <- modelGeneVarByPoisson(
            sce_delay, block=sce_delay$sample, BPPARAM=bpp
        )
        cl_stop(id)
    })
})
```

### 240 GB memory 

File id: e2874fd9-af11-4adf-a47a-f380b7606434, cell count: 19361

autoBlockSize
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("e2874fd9-af11-4adf-a47a-f380b7606434_autoBlockSize.csv")
```

Number of cpus
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("e2874fd9-af11-4adf-a47a-f380b7606434_cpu.csv")
```

File id: 7125c914-29a6-476d-ad23-949d06c371ef, cell count: 94256

autoBlockSize
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("7125c914-29a6-476d-ad23-949d06c371ef_autoBlockSize.csv")
```

Number of cpus
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("7125c914-29a6-476d-ad23-949d06c371ef_cpu.csv")
```

### 120 GB memory 

File id: e2874fd9-af11-4adf-a47a-f380b7606434, cell count: 19361

autoBlockSize
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("1bc21284-be3e-4520-9783-5a0824754b40_autoBlockSize.csv")
```

Number of cpus
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("1bc21284-be3e-4520-9783-5a0824754b40_cpu.csv")
```

File id: 7125c914-29a6-476d-ad23-949d06c371ef, cell count: 94256

autoBlockSize
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("b9500db9-31c7-40c9-94a4-e9b2dd8e6070_autoBlockSize.csv")
```

Number of cpus
```{r, echo = FALSE, message=FALSE, eval=TRUE}
read.csv("b9500db9-31c7-40c9-94a4-e9b2dd8e6070_cpu.csv")
```


## `R` session information

```{r session_info, echo=FALSE}
## Session info
library("sessioninfo")
options(width = 120)
session_info()
```
